---
title: "Assignment 1"
author: "Trisha Sukhtankar"
date: "12/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1

```{r Part 1}

library(igraph)
n <- read.csv("D:/Assignments/Sem 2/Web and Network/got-s8-nodes.csv") #importing nodes
n
names(n) <- c("name", "label")
str(n)
```

```{r }
e <- read.csv("D:/Assignments/Sem 2/Web and Network/got-s8-edges.csv")
e
names(e) <- c("source", "target", "weight", "season")
e <- e[,c(-4)]
str(e)
```

```{r}
library("scales")
e$weight<-rescale(e$weight)

g <- graph_from_data_frame(e, directed=FALSE, vertices=n) #creating undirected graph from dataframe
plot(g)
```


```{r node count}
vcount(g)

```
```{r}
ecount(g)
```
```{r strong components}
c_strong <- components(g,mode="strong")
c_strong$no
```
```{r weak components}
c_weak <- components(g,mode="weak")
c_weak$no
```

```{r diameter}
diameter(g, directed = FALSE, unconnected = TRUE, weights=NA)
```

```{r Average Path Length}
mean_distance(g,directed=FALSE,unconnected=TRUE)
```

```{r Clusturing coefficient}
transitivity(g,type="average")
```

```{r degree distribution}
d <- (degree(g, mode = "all"))
d
```

```{r degree distribution histogram}
hist(d, main="Plot 1: Degree Distribution", xlab="Degree Value", border="black",
col="#FFB0D6", xlim = c(0,50), ylim = c(0,30), breaks = 10, las=1)
```

```{r Plot 2}
hist(e$weight, main="Plot 2: Edge-Weight Distribution", xlab="Rescaled Edge weights", border="black",
col="#FFB0D6", xlim = c(0,1), breaks = 10, las=1)
```

```{r}
lyt <- layout_on_grid(g)
nodeclr<- rep(adjustcolor("gold", alpha.f = .3))
plot(g, layout = lyt, edge.color="grey", edge.width=E(g)$weight*2, vertex.color = nodeclr, vertex.frame.color="black", vertex.label = ifelse(degree(g) > 24, V(g)$label, NA), vertex.size = d, vertex.label.dist = 0, vertex.label.cex = 0.6, edge.curved = 0.2, vertex.label.color = "darkblue",main = "Plot 3: layout.grid; with selected labels" )
```
## Part 2
```{r}
d_allnodes <- degree(g,V(g),mode="all")
max(d_allnodes)
sort(d_allnodes)
```

```{r random walk}
rwalk_50 <- c() #initializing
steps_length <- c(10,50,100,200) #values of k
gr <- c() #initializing

#Using function to compute the measures of walks
compute_measure <- function(gr,start_node) {
  df_random_walk <- array(0, dim=c(4,6)) #defining dimensions of empty dataframe
colnames(df_random_walk)<- c("steps", "num_nodes", "num_edges", "diameter", "avg_path_length", "cluster") #column names of empty dataframe

df_random_walk
row <- 1 #initializing row value

  for (i in steps_length){
    random <- random_walk(gr, start= start_node, steps=i, stuck = "return")
    list_nodes <- names(random)
    random_graph <-induced_subgraph(g, list_nodes, impl = "create_from_scratch")
    df_random_walk[row,1] <- i #traversing row and column-wise to fill values in the dummy dataframe

    num_nodes <- vcount(random_graph) #counting number of nodes visited
    df_random_walk[row,2] <- num_nodes
    num_edges <- ecount(random_graph) #counting number of edges in the graph
    df_random_walk[row,3] <- num_edges
    diameter <- diameter(random_graph, directed = FALSE, unconnected = TRUE, weights=NA) #calcuating diameter

    df_random_walk[row,4] <- diameter
    avg_path_length <- mean_distance(random_graph,directed=FALSE,unconnected=TRUE)
    df_random_walk[row,5] <- avg_path_length #calculating average path length using mean_distance()
    cluster <- transitivity(random_graph,type="average") #using igraph property to calculate clustering coefficient
    df_random_walk[row,6] <- cluster
  row<-row+1
  
if(i == "50") #for random walk of 60
rwalk_50 <<- random
}
return(df_random_walk)
}
```

```{r random walk for Sansa}
#computing measures for Sansa (high degree node)

sansa_measure <- compute_measure(g,"SANSA")
sansa_measure

```

```{r}
#Dataframe for Sansa's measure
dataframe_random_walk <- NULL #initializing dataframe
dataframe_random_walk <- as.data.frame(sansa_measure,stringsAsFactors = F) #putting the computed values into a single df
dataframe_random_walk$steps <- as.numeric(dataframe_random_walk$steps) #number of steps (value of K)
dataframe_random_walk$num_nodes <- as.numeric(dataframe_random_walk$num_nodes) #number of nodes
dataframe_random_walk$num_edges <- as.numeric(dataframe_random_walk$num_edges) #number of edges
dataframe_random_walk$diameter <- as.numeric(dataframe_random_walk$diameter) #diameter
dataframe_random_walk$avg_path_length <- as.double(dataframe_random_walk$avg_path_length) #average path length

dataframe_random_walk$cluster <- as.double(dataframe_random_walk$cluster) #cluster coefficient
dataframe_random_walk
```
```{r}
#displaying in a neat table format using kable package
library(kableExtra) #complex customizable table generator
kable(dataframe_random_walk, format="html", row.names=TRUE, col.names =c( "Steps","Number of Nodes", "Number of Edges", "Diameter","Avg Path Length","Cluster Coefficient")) %>%
kable_styling(bootstrap_options = c("striped","bordered"), #bootstarpping theme to the table
full_width = T, #so that it fits to the page
font_size = 11) %>% #Font size
row_spec(1:4,bold = T, color = "green", background = "white") #font colour and background
```
```{r k vs nodes}
#Plotting k vs nodes of Sansa
library(ggplot2)
ggplot(dataframe_random_walk) +
geom_point(aes(x=steps, y=num_nodes))+
geom_line(aes(x=steps, y=num_nodes)) +
scale_x_continuous(breaks=seq(0,200,by = 50)) +
ylab("Nodes") +
xlab("Steps") +
ggtitle("Plot 4: Steps Vs Nodes for Sansa") +
theme_minimal()

```

```{r avg path length plot}
#Plotting k against no. of Avg Path Length for Tyrion
ggplot(dataframe_random_walk) +
geom_point(aes(x=steps, y=avg_path_length))+
geom_line(aes(x=steps, y=avg_path_length)) +
scale_x_continuous(breaks=seq(0,200,by = 50)) +
xlab("Steps") +
ylab("Avg Path Length") +
ggtitle("Plot 5: Steps Vs Avg Path Length for Sansa") +
theme_minimal()

```
```{r Cluster coeff plot for Sansa}
#Plotting k against no. of Clustering Coefficient for Sansa
ggplot(dataframe_random_walk) +
geom_point(aes(x=steps, y=cluster))+
geom_line(aes(x=steps, y=cluster)) +
scale_x_continuous(breaks=seq(0,200,by = 50)) +
xlab("Steps") +
ylab("Clustering Coefficient") +
ggtitle("Plot 6: Steps Vs Clustering Coefficient for Sansa") +
theme_minimal()
```

```{r Random walk for Catelyn}
catelyn_measure <- compute_measure(g,"CATELYN")
catelyn_measure
```
```{r}
##Dataframe for catelyn's measure
catelyn_random_walk<- NULL
catelyn_random_walk <- as.data.frame(catelyn_measure,stringsAsFactors = F)
catelyn_random_walk$steps <- as.numeric(catelyn_random_walk$steps)
catelyn_random_walk$num_nodes <- as.numeric(catelyn_random_walk$num_nodes)
catelyn_random_walk$num_edges <- as.numeric(catelyn_random_walk$num_edges)
catelyn_random_walk$diameter <- as.numeric(catelyn_random_walk$diameter)
catelyn_random_walk$avg_path_length <- as.double(catelyn_random_walk$avg_path_length)
catelyn_random_walk$cluster <- as.double(catelyn_random_walk$cluster)
catelyn_random_walk
```
```{r displaying Catelyn's random walk table Kable}
kable(catelyn_random_walk, format="html", row.names=TRUE, col.names =c( "Steps","Number of Nodes", "Number of Edges", "Diameter","Avg Path Length","Cluster Coefficient")) %>%
kable_styling(bootstrap_options = c("striped","bordered"), #bootstarpping theme to the table
full_width = T, #so that it fits to the page
font_size = 11) %>% #Font size
row_spec(1:4,bold = T, color = "green", background = "white") #font colour and background
```

```{r}
#Plotting k against no. of nodes for Catelyn
ggplot(catelyn_random_walk) +
geom_point(aes(x=steps, y=num_nodes))+
geom_line(aes(x=steps, y=num_nodes)) +
scale_x_continuous(breaks=seq(0,200,by = 50)) +
ylab("Nodes") +
xlab("Steps") +
ggtitle("Plot 7: Steps Vs Nodes for Catelyn") +
theme_minimal()
```

```{r}
#Plotting k against no. of Avg Path Length for Catelyn
ggplot(catelyn_random_walk) +
geom_point(aes(x=steps, y=avg_path_length))+
geom_line(aes(x=steps, y=avg_path_length)) +
scale_x_continuous(breaks=seq(0,200,by = 50)) +
xlab("Steps") +
ylab("Avg Path Length") +
ggtitle("Plot 8: Steps Vs Avg Path Length for Catelyn") +
theme_minimal()
```

```{r}
#Plotting k against no. of Clustering Coefficient for Catelyn
ggplot(catelyn_random_walk) +
geom_point(aes(x=steps, y=cluster))+
geom_line(aes(x=steps, y=cluster)) +
scale_x_continuous(breaks=seq(0,200,by = 50)) +
xlab("Steps") +
ylab("Clustering Coefficient") +
ggtitle("Plot 9: Steps Vs Clustering Coefficient for Catelyn") +
theme_minimal()
```

```{r}
#Plotting random walk of Sansa (with degree 4)
##Customizing node colour
vclr <- rep(adjustcolor("gold", alpha.f = .5), vcount(g))
# make the nodecolours of the nodes on the random walk a faded light blue
vclr[unlist(tyrion_r_walk)] <- rep(adjustcolor("lightblue", alpha.f = .5))
# Plotting the random walk graph for Tyrion's random walk with steps=50
plot(g, layout = lyt, edge.color="lightgrey", edge.width=0.2, vertex.color = vclr, vertex.frame.color="black", edge.curved = 0.2,vertex.size = deg, vertex.label = ifelse(V(g)$name == "TYRION", V(g)$label, NA), vertex.label.dist = 0, vertex.label.cex = 0.7, vertex.label.color = "darkblue", main = "Plot 10: Tyrion's Random Walk over 50 steps" )